Better Splitting Algorithms for Parallel Corpus Processing

### 2012-08-09 doc/latex/paper.tex
Fixed three minor problems after final re-read.

\begin{algorithm}[!h]
\caption{Split input text into $n$ parts to balance the histograms of line lengths for all parts.}
\begin{algorithmic}
\fontspec{TeX Gyre Pagella}
\Function{\fontspec{TeX Gyre Pagella}\textsc{Histogram-Split}}{$n$,input}
\For {$i \gets 0 \ldots ($ input.length $-1)$}
\State sentence[$i$].length $\gets$ input[$i$].length
\State sentence[$i$].index $\gets i$
\EndFor
\State \Call{Sort}{sentence} $\left\{|x,y|\ x.\mbox{length}\Leftrightarrow y.\mbox{length}\right\}$ 
\State \Comment{Sort sentences by length}
\State $p \gets n$
\For {$i \gets 0 \ldots ($input.length $-1)$}
\If {$p < n$}
\State $p \gets p+1$
\Else
\State $p \gets 0$
\EndIf
\State output[$p$].append(input[sentence[$i$].index])
\EndFor
\State \textbf{return} output
\EndFunction
\end{algorithmic}
\label{alg:histogram}
\end{algorithm}

@@

%\vspace{-0.2cm}
\section{Conclusion}
%\vspace{-0.1cm}
%The task of translation involves translating a source language document into a target language. 
%
While statistical translation models could, in theory, condition on previously translated sentences, in practice virtually no widely used models do so.
%
%The task of translating a document is therefore embarrassingly parallel.
Translation is therefore embarrassingly parallel ---
%
a document to be translated can be split into $n$ parts, with each part translated independently a different computational node.

While such splitting is commonly performed, a suboptimal naive splitting technique (Algorithm \ref{alg:naive}) is used by all translation software of which we are aware. 
%
In this work we have presented three more effective corpus splitting algorithms (Algorithms \ref{alg:histogram}, \ref{alg:words} and \ref{alg:times}), 
%the Moses decoding scripts,
%{\tt moses-parallel.pl},
% 
enabling substantial speed-ups in parallel decoding time at no additional cost.

>>>>

\begin{algorithm}[!h]
\caption{Split input text into $n$ parts to balance the histograms of line lengths for all parts.}
\begin{algorithmic}
\fontspec{TeX Gyre Pagella}
\Function{\fontspec{TeX Gyre Pagella}\textsc{Histogram-Split}}{$n$,input}
\For {$i \gets 0 \ldots ($ input.length $-1)$}
\State sentence[$i$].length $\gets$ input[$i$].length
\State sentence[$i$].index $\gets i$
\EndFor
\State \Call{Sort}{sentence} $\left\{|x,y|\ x.\mbox{length}\Leftrightarrow y.\mbox{length}\right\}$ 
\State \Comment{Sort sentences by length}
\State $p \gets n$
\For {$i \gets 0 \ldots ($input.length $-1)$}
\If {$p < n-1$}
\State $p \gets p+1$
\Else
\State $p \gets 0$
\EndIf
\State output[$p$].append(input[sentence[$i$].index])
\EndFor
\State \textbf{return} output
\EndFunction
\end{algorithmic}
\label{alg:histogram}
\end{algorithm}

@@

%\vspace{-0.2cm}
\section{Conclusion}
%\vspace{-0.1cm}
%The task of translation involves translating a source language document into a target language. 
%
While statistical translation models could, in theory, condition on previously translated sentences, in practice virtually no widely used models do so.
%
%The task of translating a document is therefore embarrassingly parallel.
Translation is therefore embarrassingly parallel ---
%
a document to be translated can be split into $n$ parts, with each part translated independently on a different computational node.

While such splitting is commonly performed, a suboptimal naive splitting technique (Algorithm \ref{alg:naive}) is used by all translation software of which we are aware. 
%
In this work we have presented three more effective corpus splitting algorithms (Algorithms \ref{alg:histogram}, \ref{alg:words} and \ref{alg:times}), 
%the Moses decoding scripts,
%{\tt moses-parallel.pl},
% 
enabling substantial speed-ups in parallel decoding time at virtually no additional cost.
